Naturalness in U(1) extensions of the MSSM

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Changed discussion on fig 2 a bit.

% DH:: I'm not sure if this is worth including? I've put a disclaimer in the
% text, as well.
\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{mssm_higgs_tuning.png}}
\caption{Scatter plot of fine tuning in the MSSM as a function of
the lightest Higgs mass, $m_{h_1}$, for the cut-off scales (from 
bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
\label{Fig:mssmhiggstuning}
\end{center}
\end{figure}
To illustrate this, in Fig.~\ref{Fig:mssmstoptuning} we show the
variation in fine tuning when we scan over the stop masses and mixing,
with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and
$-3810\textrm{ GeV}\leq A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV,
$50$ TeV and $100$ TeV.  The remaining parameters we fix such that at
$M_{SUSY}$ they have the values $\mu=-97.5$ GeV, $B=-84.8$ GeV,
$M_1=92.1$ GeV, $M_2=95.9$ GeV, $M_3=352$ GeV, $A_b=-117.9$ GeV,
$A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV, $m_{e_i}=204$ GeV,
$m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and $m_{d_i}=438$ GeV
($i=1,2,3$). By making this choice for the remaining parameters we
ensure that fine tuning due to each is small, so that we avoid washing
out the fine tuning impact of the stops when the tuning is
small \footnote{For models in which the spectrum is heavier, when the
  stop masses become very small the fine tuning reaches a lower bound
  imposed by other heavier parameters.} as can be the case when the
stop masses are less than 1 TeV.  Note that the Higgs mass is also
allowed to vary over the scan, as shown in
Fig.~\ref{Fig:mssmhiggstuning}.  However this tuning only really
becomes large for very large stop masses.  On the other hand if the
cuttoff is increased then stop masses of several TeV can result in
tuning of [insert] as shown in Fig.~\ref{Fig:mssmstoptuning}.\\ \\

>>>>

% DH:: I'm not sure if this is worth including? I've put a disclaimer in the
% text, as well.
\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{mssm_higgs_tuning.png}}
\caption{Scatter plot of fine tuning in the MSSM as a function of
the lightest Higgs mass, $m_{h_1}$, for the cut-off scales (from 
bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
\label{Fig:mssmhiggstuning}
\end{center}
\end{figure}
To illustrate this, in Fig.~\ref{Fig:mssmstoptuning} we show the
variation in fine tuning when we scan over the stop masses and mixing,
with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and
$-3810\textrm{ GeV}\leq A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV,
$50$ TeV and $100$ TeV.  The remaining parameters we fix such that at
$M_{SUSY}$ they have the values $\mu=-97.5$ GeV, $B=-84.8$ GeV,
$M_1=92.1$ GeV, $M_2=95.9$ GeV, $M_3=352$ GeV, $A_b=-117.9$ GeV,
$A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV, $m_{e_i}=204$ GeV,
$m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and $m_{d_i}=438$ GeV
($i=1,2,3$). Although we should stress that making this choice will
lead to a spectrum which is in conflict with the LHC limits, doing so
ensures that fine tuning due to the other parameters is small, so that
we avoid washing out the fine tuning impact of the stops when the
tuning is small \footnote{For models in which the spectrum is heavier,
  when the stop masses are small the fine tuning reaches a lower bound
  imposed by other heavier parameters.} as can be the case when the
stop masses are less than 1 TeV.  Note that the Higgs mass is also
allowed to vary in this scan, as shown in
Fig.~\ref{Fig:mssmhiggstuning}. This reveals the tuning problem which
people have been worrying about since the discovery of the 125 GeV
Higgs boson as we see that raising the stop masses is also pushing up
the Higgs mass, meaning that heavier Higgs masses require more fine
tuning.  However for a low value of the UV scale this tuning is not so
severe unless the stops are very heavy, and a 125 geV Higgs can be
obtained without much tuning in this unrealistic case where we have
minimised other sources of tuning.  On the other hand the tuning
becomes more severe as we increase the cuttoff such that for $M_X =
10^{16}$ GeV is increased then a lightest stop masses of 1-3 TeV can
result in a fine tuning of $\approx 200 - 1000$ as shown in
Fig.~\ref{Fig:mssmstoptuning} and the minimum tuning we see consistent with a $125$ GeV Higgs is $\approx 200$.\\ \\
